The role of advection versus diffusion in intraventricular transport

### 2025-02-04 paper/main.tex
Department of
add geometry percentage changes

% Title
\title{The role of advection versus diffusion in intraventricular transport}
\author[1,*]{Halvor Herlyng}
\author[1]{Ada J.~Ellingsrud}
\author[1]{Miroslav Kuchta} 
\author[X]{Inyoung Jeong} % OK?
\author[1,3,+]{Marie E.~Rognes} % OK order?
\author[2,+, *]{Nathalie Jurisch-Yaksi}
\affil[1]{Department for Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
\affil[2]{Department of Clinical and Molecular Medicine, Norwegian University of Science and Technology, Trondheim, Norway}
\affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no} \href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
\affil[+]{these authors contributed equally to this work}
% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={zebrafish-cilia-csf},
  pdfauthor={H.~Herlyng~\emph{et al.}}
}
\fi

@@

The morphology and geometry of the brain ventricles vary across zebrafish
individuals, and under physiological and pathological conditions. 
Motivated by an interest in how geometry impacts solute distribution,
we also consider four variations in the ventricular geometry: by shrinking the fore-mid brain connection, 
the middle ventricle, the mid-hind brain connection, and all three simultaneously. 
We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
\mer{MER: More specifics (i.e.~1 sentence and/or inserted info) here on how much these were shrunk and how.}

>>>>

% Title
\title{The role of advection versus diffusion in intraventricular transport}
\author[1,*]{Halvor Herlyng}
\author[1]{Ada J.~Ellingsrud}
\author[1]{Miroslav Kuchta} 
\author[X]{Inyoung Jeong} % OK?
\author[1,3,+]{Marie E.~Rognes} % OK order?
\author[2,+, *]{Nathalie Jurisch-Yaksi}
\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
\affil[2]{Department of Clinical and Molecular Medicine, Norwegian University of Science and Technology, Trondheim, Norway}
\affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no} \href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
\affil[+]{these authors contributed equally to this work}
% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={zebrafish-cilia-csf},
  pdfauthor={H.~Herlyng~\emph{et al.}}
}
\fi

@@

The morphology and geometry of the brain ventricles vary across zebrafish
individuals, and under physiological and pathological conditions. 
Motivated by an interest in how ventricular geometry impacts solute distribution,
we also consider four variations in the geometry \fixme{(percentage reduction in cross-sectional areas):
by shrinking the fore-mid brain connection (66 \%), 
the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.} 
We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
